---
title: "Data viz-iris"
author: "A L M Salahuddin"
date: "1/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
df<-read.csv("Iris.csv")

```

First, I will load the dataset.
```{r}
df <- read.csv('Iris.csv')
cols <- c('SepalLenth','SepalWidth','PedalLength','PedalWidth','Class')
colnames(df)<-cols
df%>%head
```
```{r}
summary("Iris.csv")
```

Now, I will get the summary for SepalLenth.

```{r}
summary(df$SepalLenth)
```
 
Next find outh the mean for SepalLenth.

```{r}
mean(df$SepalLenth)
```


# Box plots

I will visualize box plot for the class data.

```{r}
boxplot(df$Class)
```

# Histogram

I will visualize histogram plot for the PedalLength data.

```{r}
ggplot(df, aes(x= PedalLength)) +
  geom_histogram(bin=10)
```

# Box plot

I will visualize another box plot for the PedalLength data.

```{r}
boxplot(df$PedalLength)
```

# violin plot

Next, I will visualize another violin plot for the PedalLength data.

```{r}
ggplot(df, aes(x=Class, y=PedalLength)) + 
  geom_violin(trim=FALSE)
```

```{r}
sd(df$PedalLength)
```

